### 2024-03-25 Scripts/Manuscript/manuscript.Rmd
adjusted appendices and Discussion section.

  Enter author note here. Caspar/Jelte/Marjan?

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this study assessed these influences in large scale replication projects. 
  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects. 
  The quality of measurement reporting in replication protocols did however relate to replicability.
  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "194"

@@

\renewcommand{\topfraction}{.85}

@@

\renewcommand{\bottomfraction}{.7}

@@

\renewcommand{\floatpagefraction}{.66}

<!-- min fraction of page that should have floats -->

@@

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. Another factor which has gained more traction recently are measurement related issues' impact on replicability. In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

@@

Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure. Questionable Measurement Practices (QMPs) are practices that decrease the information that is necessary to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMP and replicability.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

## Questionable Measurement Practices
A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement]. Any scientific report should therefore clearly motivate the use of measure and procedure. Without clear reporting on these aspects, the validity of measurement will remain uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

@@

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research [^1]. Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.

@@

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = number of, IQR = Interquartile range.")
```

@@

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
  , escape = FALSE, placement= "htp", booktabs = TRUE)

@@

Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.

@@

```{=tex}
\begin{equation}
QMP_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
\end{equation}
```

@@

```{=tex}
\begin{equation}
QMP_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in Appendix D.

@@

Every hypothesis test in this study used an alpha significance cutoff of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as they deemed less harmful to the exploratory aims of this study.

@@

@@

After the pre-registration was registered, and data had been collected and analysed, it came to the author's attention that it is possible to conduct meta-analyses on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis]. Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook]. Subsequently, the true variation in the metric, or heterogeneity, can be tested to constitute a significant part of the total variation in the observed estimates of the metric or not.

Because heterogeneity estimates line up well as a test for hypothesis 2, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable. The rma function from metafor package [@R-metafor] was used to run the meta-analysis. No correction for bias or weighting of the effects has been implemented, to reduce model complexity, and because the data came from Many Labs replication projects and not typical literature.

A meta-analysis requires an estimate of the standard error in order to be conducted. For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError was used to calculate alpha's standard error. Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.

@@

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study. For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome[^4].

[^4]: This analysis was changed from the pre-registered analysis. In the pre-registered analysis a beta-regression was used to model the same relation, only with replication success as the predictor variables and replication QMP ratio as the outcome. The outcome was swapped in the article for the sake of interpretability. The results based on the original analyses are presented in Appendix A.

@@

The relationship between original article QMPs and replication protocol QMPs was modeled to test hypothesis 6. The outcome variable is the same as the predictor in the model for hypothesis 5. The independent variable in this model is instead the QMP ratio for the original articles. The resulting model formula is as follows:

@@

## Data Visualization
This study's focus is mainly exploratory and descriptive. Additionally, the number of coded and extracted data is quite substantial. Therefore, the result section will start with a number of visuals and descriptives to provide some clarity on the data and its characteristics.

@@

Despite the lack of reliability reporting,if scalar data could be accessed for a measure the reliability could be calculated for each lab it was used in. The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication. The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.

@@

```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.

```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol. The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPS, grey means modification did not occur for that measure. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}

@@

# total QMP ratios
Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

@@

Table \@ref(tab:MeasurementReportingDescriptivesTable) shows additional descriptive information on measurement reporting based on counts of reported information that were not used to calculate QMP ratios. When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `rnrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).

@@

The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`. Because this number is larger than .5, it suggests that variance was larger between replication sets than within.

@@

However, since the Q-test is sensitive to the number of studies in the meta-analyses [@li2015DilemmaHeterogeneityTests], some of the discrepancy in the estimate of heterogeneity based on this test may in part be due to the fact that for some measures the sample size of labs that used them was too low. Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence id inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.

@@

The logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`). Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix D). These results are contradictory to the expectation in hypothesis 3. However, the reliability coefficient could be calculated for only a small sample number of measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty and remains inconclusive.

@@

## Limitations & Future Research

>>>>

  Enter author note here. Jelte/Marjan?

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this study assessed the influences of poor measurement reporting in replications from the Many Labs replication projects, and the original articles that the replications were based on, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. 
  Here we show that while contrary to expectations reliability did not relate to replicability, the quality of measurement reporting in replications did relate. 
  For original articles the quality was indirectly related to replicability through the quality of measurement reporting in replications.
  These and other descriptive results indicate similarly to previous research that measurement details in both original research and replications are underreported.
  However, some of the issues in measurement reporting that were identified as most critical in this study differ from what has been stated in previous research.
  Measurement is a crucial part of almost all empirical research, it's details should tehrefore be transparently reported to enable critical evaluation and independent replication.
  Consequently, recommendations are given to researchers and replicators on the measurement practices that are  most crucial to improve on.. 
  Finally, directions are given for future research to further investigate the (causal) relationship between measurement practices and replicability.

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "234"

@@

\renewcommand{\topfraction}{.8}

@@

\renewcommand{\bottomfraction}{.8}

@@

\renewcommand{\floatpagefraction}{.8}

<!-- min fraction of page that should have floats .66 -->

@@

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings led to the claim that psychology was facing a 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is needed to evaluate the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. Another factor which has gained more traction recently are measurement related issues' impact on replicability. In particular, studies shown that measurement error and questionable measurement practices may impact replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

@@

Even when ignoring reliability, a measurement's content and implementation still need to validly capture what it intends to measure. Questionable Measurement Practices (QMPs) are practices that decrease the availability of information needed to evaluate a measurement's validity, and have been coined as a conjugate term to QRPs. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of both measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings on data from real replications. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study additionally aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by exploratively investigating the relation between QMPs and replicability.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardizing impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centered around the testing of heterogeneity in replications [@klein2018many]. However analyses from this Many Labs, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

## Questionable Measurement Practices
A measure not only needs to be reliable, it should also in its design and implementation adequately capture what it intends to measure [@flake2020measurement]. Any scientific report should therefore clearly motivate the use of measure and procedure. When these aspects are not clearly reported on, the validity of measurement remains uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

@@

The total number of identified psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of `r sum(table(coded_data_replications$many_labs_version, coded_data_replications$appearance)[,1])`. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the key unit of analysis. Here primary measures refers to measures assessing variables included in the primary test of the replication. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of `r nrow(coded_data_replications)` measures used in both original and replication research[^1]. Table \@ref(tab:ManyLabsDescriptivesTable) shows further descriptive information about the data for each Many Labs Project.

@@

# print the table in apa formatting
apa_table(
  many_labs_descriptives_table, align = c("l", "r", "r", "r", "r", "r", "r"), escape = FALSE, placement = "htp", midrules = 4, caption = "General Descriptives of the Many Labs Projects"
  , note = "$^a$ refers only to the number of identified primary measures, which this study is concerned with. Rep. = Replicaiton, Org. = Original., N = total number of, IQR = Interquartile range.")
```

@@

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# making the column names look less robot speak-y.
colnames(QMP_info_dataframe) <- c("CategorWy", "N Questions", "Example Question")

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions considered used for calculating QMP ratios."
  , escape = FALSE, placement= "htp", booktabs = TRUE)

@@

Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Further details on all the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.

@@

```{=tex}
\begin{equation}
QMP\_ratio_{j} = \frac{\sum_{n=1}^i True_{ij}}{\sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioType)
\end{equation}
```

@@

```{=tex}
\begin{equation}
QMP\_ratio = \frac{\sum_{n=1}^j \sum_{n=1}^i True_{ij}}{\sum_{n=1}^j \sum_{n=1}^i True_{ij} + False_{ij}} (\#eq:QMPRatioTotal)
\end{equation}
```

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly too stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages. The analyses, tables and figures presented in this article are all based on the revised coding protocol, the equivalent results based on QMPs obtained with the initial protocol can be found in Appendix D.

@@

@@

Every hypothesis test in this study used an alpha significance cutoff of .05. No correction for multiple testing was applied, to ensure that the rate of false negatives remained low, the increase in false positive rate was accepted as less harmful to the exploratory aims of this study.

@@

After data had been collected and analysed, it came to the author's attention a meta-analyses could be conducted on reliability coefficients, commonly referred to as Reliability Generalization Meta-Analyses [@botella2012ManagingHeterogeneityVariance; @lopez-ibanez2024ReliabilityGeneralizationMetaanalysis]. Using meta-analysis, it is possible to quantify within the model the degree of true variation in the metric of interest across samples [@cooper2019handbook].

In order to test whether or not the true variation in the metric, or heterogeneity, constituted a significant part of the total variation in the observed estimates of the metric or not, a random-effects meta-analysis was conducted on the calculated Cronbach's alpha for each measure for which replication datasets were available and usable. The rma function from metafor package [@R-metafor] was used to run the meta-analysis. No correction for bias or weighting of the effects was implemented, to reduce model complexity, and because the data from the Many Labs replication projects do not reflect a typical literature.

A meta-analysis requires an estimate of the standard error in order to be conducted. For Cronbach's alpha, formulas 2 & 3 from @duhachek2004AlphaStandardError were used to calculate alpha's standard error. Heterogeneity was estimated using the tau value, meaning the standard deviation of the distribution of true Cronbach's alpha coefficients for that measure, and tested using the Cochran's Q test for each measure.

@@

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study. For hypothesis 5 the QMP ratio was used as the predictor for replication success, while replication success was used as the outcome.

@@

The relationship between original article QMPs and replication protocol QMPs was modeled to test hypothesis 6. The outcome variable is the same as the predictor in the model for hypothesis 5. The independent variable in this model is instead the QMP ratio for the original articles[^4]. The resulting model formula is as follows:

[^4]: This analysis was not pre-registered. Only the analyses for each combination of QMP types were pre-registered and can be found in appendix A, however all analyses of hypothesis 6 were originally planned to use contingency tables with no inferential test. This was changed quickly after the study was pre-registered to using beta-regression as is done here and in appendix A.

@@

## Data Visualization
This study's focus is mainly exploratory and descriptive. Additionally, the number of coded and extracted data is quite substantial. Therefore, the result section will start with a number of descriptives and figures to provide an overview of the data.

@@

If scalar data could be accessed for a measure, the reliability could also be calculated from the replication data for each lab. The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication. The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.

@@

```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure. Meta-analyses for which the Q-test for heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displayed, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check_REV)["True"])` out of `r apa_num(nrow(coded_data_replications))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check_REV)["True"], numerals = FALSE)` measures used in original studies were modified.

```{r Plot456Code, warning = FALSE, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by whether the QMP ratio was obtained from an original article or a replication protocol. The top row shows for each QMP type the proportions of each QMP ratio obtained, darker colours represent proportionally more QMPs, grey means modification did not occur for that measure. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}

@@

# total QMP ratios
Plot_456_2 <- ggplot(plot_456_data[plot_456_data$QMP_type == "Total",], 
       aes(x = QMP_ratio_REV, fill = RepOrg, colour = RepOrg)) +
  geom_density(alpha = 0.2) +
  geom_point(y = 0, alpha = 0.2, size = 3) +
  geom_segment(aes(x = Mean_Rat_Rep, xend = Mean_Rat_Rep, y = 0, yend = 2.66)
               , color = "blue4") +
  geom_segment(aes(x = Mean_Rat_Org, xend = Mean_Rat_Org, y = 0, yend = 2.183)
               , color = "brown") +
  coord_cartesian(xlim = c(0, 1)) +
  theme_ridges() + 
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.x = element_text(size = 8)) +
  scale_fill_manual(values=c("brown", "blue4")) +
  scale_color_manual(values=c("brown2", "blue")) +
  scale_x_continuous(breaks = c(0, Mean_Rat_Rep, 0.25, Mean_Rat_Org, 
                                0.5, 0.75, 1), 
                     labels = c("0", "0.18", "0.25", "0.31", "0.5", 
                                "0.75", "1")) + 
  ggtitle("Distribution of Total QMP Ratio's by Original and Replication") +
  guides(color = "none") +
  labs(fill = "Coded from") +
  ylab("") +
  xlab("")

@@

Table \@ref(tab:MeasurementReportingDescriptivesTable) shows additional descriptive information on measurement reporting based on counts of reported information that were not used to calculate QMP ratios. When it was not stated that existing materials were used, it was expected that the remaining articles would clearly specify that they newly created the materials, however this was not always the case for neither original articles (`r table(coded_data_original_shortened$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_original_shortened) - table(coded_data_original_shortened$sel_existing)[["True, namely:"]]` relevant measures) nor replication protocols (`r table(coded_data_replications$sel_existing)[["False, materials were newly developped for this study"]]` out of `r nrow(coded_data_replications) - table(coded_data_replications$sel_existing)[["True, namely:"]]` relevant measures).

@@

The ICC of the between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient was approximately `r apa_num(ICC_alpha, digits = 3)`. Because this number is larger than .5, it suggests that the majority of the total variance in the calculated Cronbach's alpha was between replication sets rather than within.

@@

However, since the Q-test is sensitive to the number of studies in the meta-analyses [@li2015DilemmaHeterogeneityTests], some of the discrepancy in the estimate of heterogeneity based on this test may in part be due to the fact that for some measures the sample size of labs that used them was too low. Therefore, while consistent evidence for heterogeneity would imply true variance in Cronbach's alpha within replication sets would run counter to hypothesis 2, the evidence is inconsistent when looking across all studies, and remains sensitive to the sample size in the meta-analyses.

@@

The logistic model indicated that Cronbach's alpha did not significantly relate to replication success in the main logistic regression model (Cronbach's alpha: `r H3_main_full_results_alpha_with_OR`). Similar results were found based on the calculated omega coefficient (see Appendix C) and in all of the multilevel sensitivity analyses models (see Appendix B). These results are contradictory to the expectation in hypothesis 3. However, the reliability coefficient could be calculated for only a small sample number of measures. As a result, the estimates of the relation between reliability and replication success obtained using these models each come with large uncertainty and remains inconclusive.

@@

What did not appear to affect the replicability of a study was the reliability of the measure used in the study. This result is surprising, given that @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error. The significance test cut-off criteria that was used in this study to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected. However contrary to both Hypothesis 3 and @stanley2014expectations, less reliable measures were not associated with a decrease in replicability.
